### 2013-05-31 context-dependence.tex
cpg?

\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath,amssymb}
\usepackage{amsthm}

@@

>>>>

\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath,amssymb}
\usepackage{amsthm}
\usepackage{graphicx}

@@

%%%%%%%
\section{Simulation results}

The method works well to find point estimates of the parameters.
Obtaining posterior density estimates using the approximation likelihood function on a subset of patterns
works in some cases;
in other cases the likelihood surface is still too peaked, underestimating the uncertainty.

\subsection{TASEP}

Strings of length $10^5$ were evolved under TASEP for varying amounts of time,
and pattern occurrences counted.
Running 10,000 MCMC iterations with window sizes of $\ell=w=3$ (total length 9) on these takes around 40 minutes.
Apparently, the patterns used were not sufficiently independent in this case,
as the posterior is too sharp.

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{tasep/all-mcmc-runs}
  \end{center}
  \caption{ Results from MCMC estimates of the parameter in TASEP (mutation rate multiplied by time).  
  Vertical line shows the true value.
  }
\end{figure}

\subsection{Ising model}

Strings of length $10^6$ were evolved under Glauber dynamics on the Ising model with varying parameters,
and pattern occurrences counted.
As for TASEP, unning 10,000 MCMC iterations with window sizes of $\ell=w=3$ (total length 9) on these takes around 40 minutes.
In this case, the true parameter values have good distribution within the estimated posterior distributions.

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,page=1]{ising/all-mcmc-runs}
  \end{center}
  \caption{ Results from MCMC estimates of the mutation rate parameter in the Ising model (scaled by amount of time). 
  Vertical line shows the true value.
  }
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,page=2]{ising/all-mcmc-runs}
  \end{center}
  \caption{ Results from MCMC estimates of the inverse temperature $\beta$ in the Ising model. 
  Vertical line shows the true value.
  }
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,page=3]{ising/all-mcmc-runs}
  \end{center}
  \caption{ Results from MCMC estimates of the magenization parameter in the Ising model. 
  Vertical line shows the true value.
  }
\end{figure}

%%%%%%%%
\section{What next}

\begin{enumerate}

  \item Do inference along a tree.

  \item See if counting in nonoverlapping windows fixes the peakiness problem with TASEP.

  \item See what's feasible with a larger alphabet -- 4 bases, or 20 amino acids -- and more parameters.

  \item Show that taking $\ell=0$ can be positively misleading (when?).

\end{enumerate}
